### 2020-02-26 paper2/paper.tex
To send for examination (oppo/comm).

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Flow-assisted droplet assembly in a 3D microfluidic channel] % Short title used in headlines (optional)
{%
  Flow-assisted droplet assembly in a 3D microfluidic channel% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Flow-assisted droplet assembly in a 3D microfluidic channel} % Title for toc
%
\paperauthor[Ge, Tammisola, Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge, Outi Tammisola, Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, O. Tammisola, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Soft Matter.] % Short publish info used in List Of Papers
{%
	Soft Matter%
}%
%
\papervolume{15}%
%
\papernumber{}%
%
\paperpages{3451--3460}%
%
\paperyear{2019}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
In this paper, we perform a series of simulations using methods developed in \emph{Paper 1}
to examine the droplet interactions in increasingly realistic conditions, mimicking a microfluidic experiment.
The main objective is to elucidate the physical mechanism that leads to the experimentally observed droplet clustering,
which had been explained by a dipolar interaction theory.
Contrary to previous belief, we find that dipolar interactions alone cannot account for the fast droplet rearrangement;
a number of 3D effects, which are hard to model at once, must be included to faithfully reproduce the observation.
This conclusion is supported by theoretical derivations of particle interactions in Stokes flow (\emph{Papers 3 \& 4}),
suggesting that designing optimal microfluidic channels to directly produce large droplet crystals remains difficult in practice.
}%
%
\graphicspath{{paper2/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Flow-assisted droplet assembly in a 3D microfluidic channel] % Short title used in headlines (optional)
{%
  Flow-assisted droplet assembly in a 3D microfluidic channel% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Flow-assisted droplet assembly in a 3D microfluidic channel} % Title for toc
%
\paperauthor[Ge, Tammisola, Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge, Outi Tammisola, Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, O. Tammisola, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Soft Matter.] % Short publish info used in List Of Papers
{%
	Soft Matter%
}%
%
\papervolume{15}%
%
\papernumber{}%
%
\paperpages{3451--3460}%
%
\paperyear{2019}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
In this paper, we perform a series of simulations using methods developed in \emph{Paper 1}
to examine the droplet interactions in increasingly realistic conditions, mimicking a microfluidic experiment.
The main objective is to elucidate the physical mechanism that leads to the experimentally observed droplet clustering,
which had been explained by a dipolar interaction theory.
Contrary to previous belief, we find that dipolar interactions alone cannot account for the fast droplet rearrangement;
a number of 3D effects, which are hard to model at once, must be included to faithfully reproduce the observation.
This conclusion is supported by theoretical derivations of particle interactions in Stokes flow (\emph{Papers 3 \& 4}),
suggesting that designing optimal microfluidic channels to directly produce large droplet crystals is more of an art than science in practice.
}%
%
\graphicspath{{paper2/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

### 2020-02-26 paper3/paper.tex
To send for examination (oppo/comm).

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Integral representation of channel flow with interacting particles] % Short title used in healines (optional)
{%
 Integral representation of channel flow with interacting particles% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Integral representation of channel flow with interacting particles} % Title for toc
%
\paperauthor[Fouxon, Ge, Brandt, Leshansky] % Short authors used in headlines and List Of Papers
{%
  Itzhak Fouxon$^{1,2}$, Zhouyang Ge$^3$, Luca Brandt$^3$, \\Alexander Leshansky$^1$%
}%
%
\listpaperauthor{I. Fouxon, Z. Ge, L. Brandt, A. Leshansky}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Department of Chemical Engineering, Technion, Haifa 32000, Israel\\%
  $^2$ Department of Computational Science and Engineering, Yonsei University, \\Seoul 120-749, South Korea\\%
  $^3$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Phys.\ Rev.\ E.] % Short publish info used in List Of Papers
{%
	Physical Review E%
}%
%
\papervolume{96}%
%
\papernumber{063110}
%
\paperpages{}%
%
\paperyear{2017}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   In this first part of a two-part theoretical work on droplet interactions,
   we consider the far-field interaction of spherical droplets or particles traveling in the Poiseuille flow.
   A boundary integral representation of the disturbance flow is derived,
   showing that, to leading order, the flow is dipolar and proportional to a weighted integral of the stress and flow at the particle surface.
   We tabulate the dipole moment under various confinement and particle initial positions by directly simulating a rigid particle in fully-resolved channel flow,
   using a second-order accurate immersed boundary method.
   Analytically, we also introduce the equation of motion that describes hydrodynamic interactions and solve it in the cases of two and three particles. 
}%
%
\graphicspath{{paper3/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Integral representation of channel flow with interacting particles] % Short title used in healines (optional)
{%
 Integral representation of channel flow with interacting particles% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Integral representation of channel flow with interacting particles} % Title for toc
%
\paperauthor[Fouxon, Ge, Brandt, Leshansky] % Short authors used in headlines and List Of Papers
{%
  Itzhak Fouxon$^{1,2}$, Zhouyang Ge$^3$, Luca Brandt$^3$, \\Alexander Leshansky$^1$%
}%
%
\listpaperauthor{I. Fouxon, Z. Ge, L. Brandt, A. Leshansky}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Department of Chemical Engineering, Technion, Haifa 32000, Israel\\%
  $^2$ Department of Computational Science and Engineering, Yonsei University, \\Seoul 120-749, South Korea\\%
  $^3$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Phys.\ Rev.\ E.] % Short publish info used in List Of Papers
{%
	Physical Review E%
}%
%
\papervolume{96}%
%
\papernumber{063110}
%
\paperpages{}%
%
\paperyear{2017}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   In this first part of a two-part theoretical work on droplet interactions,
   we consider the far-field interaction of spherical droplets or particles traveling in the Poiseuille flow.
   A boundary integral representation of the disturbance flow is derived,
   showing that, to leading order, the flow is dipolar and proportional to a weighted integral of the stress and flow at the particle surface.
   We tabulate the dipole moment under various confinement and particle initial positions by directly simulating a rigid particle in fully-resolved channel flow
   using a second-order accurate immersed boundary method.
   Analytically, we also introduce the equation of motion that describes hydrodynamic interactions and solve it in the cases of two and three particles. 
}%
%
\graphicspath{{paper3/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

### 2020-02-26 paper4/paper.tex
To send for examination (oppo/comm).

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Two spheres in wall-bounded shear flow] % Short title used in healines (optional)
{%
 The theory of hydrodynamic interaction of \\two spheres in wall-bounded shear flow% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{The theory of hydrodynamic interaction of two spheres in wall-bounded shear flow} % Title for toc
%
\paperauthor[Fouxon, Rubinstein, Ge, Brandt, Leshansky] % Short authors used in headlines and List Of Papers
{%
  Itzhak Fouxon$^{1,2}$, Boris Rubinstein$^3$, Zhouyang Ge$^4$, \\Luca Brandt$^4$, Alexander Leshansky$^1$%
}%
%
\listpaperauthor{I. Fouxon, B. Rubinstein, Z. Ge, L. Brandt, A. Leshansky}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Department of Chemical Engineering, Technion, Haifa 32000, Israel\\%
  $^2$ Department of Computational Science and Engineering, Yonsei University, \\Seoul 120-749, South Korea\\%
  $^3$ Stowers Institute for Medical Research, 1000 E 50th st., Kansas City, \\MO 64110, USA\\%
  $^4$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Under review for Phys.\ Rev.\ Fluids] % Short publish info used in List Of Papers
{%
	Under review for Physical Review Fluids%
}%
%
\papervolume{}%
%
\papernumber{}
%
\paperpages{}%
%
\paperyear{}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   In the second part of the theoretical investigation on droplet interactions in shear flow,
   we revisit the classical work of \cite{batchelor_green_1972}, where two spherical particles interact hydrodynamically in a unbounded linear flow.
   Using the boundary integral formulation derived in \emph{Paper 3},
   we show that the inclusion of a distant wall results in qualitatively different particle trajectories, demonstrative of the wall's singular perturbation.
   Specifically, the distance at which the wall significantly alters the particles interaction scales as $z_0^{3/5}$,
   where $z_0$ is the initial distance between the particle and the wall.
   The phase portrait of the particle relative paths admits domains of closed (dancing) and open (swapping) trajectories,
   apart from those that also exist in unbounded shear flows.
   We postulate that the patterns are topologically stable and verified it by direct numerical simulations of the Navier-Stokes equations.
   Qualitatively, the distant wall is the third body that changes the global topology of the phase portrait of two-particle interaction.
}%
%
\graphicspath{{paper4/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Two spheres in wall-bounded shear flow] % Short title used in healines (optional)
{%
 The theory of hydrodynamic interaction of \\two spheres in wall-bounded shear flow% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{The theory of hydrodynamic interaction of two spheres in wall-bounded shear flow} % Title for toc
%
\paperauthor[Fouxon, Rubinstein, Ge, Brandt, Leshansky] % Short authors used in headlines and List Of Papers
{%
  Itzhak Fouxon$^{1,2}$, Boris Rubinstein$^3$, Zhouyang Ge$^4$, \\Luca Brandt$^4$, Alexander Leshansky$^1$%
}%
%
\listpaperauthor{I. Fouxon, B. Rubinstein, Z. Ge, L. Brandt, A. Leshansky}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Department of Chemical Engineering, Technion, Haifa 32000, Israel\\%
  $^2$ Department of Computational Science and Engineering, Yonsei University, \\Seoul 120-749, South Korea\\%
  $^3$ Stowers Institute for Medical Research, 1000 E 50th st., Kansas City, \\MO 64110, USA\\%
  $^4$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Under review for Phys.\ Rev.\ Fluids] % Short publish info used in List Of Papers
{%
	Under review for Physical Review Fluids%
}%
%
\papervolume{}%
%
\papernumber{}
%
\paperpages{}%
%
\paperyear{}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   In the second part of the theoretical investigation on droplet interactions in shear flow,
   we revisit the classical work of \cite{batchelor_green_1972}, where two spherical particles interact hydrodynamically in a unbounded linear flow.
   Using the boundary integral formulation derived in \emph{Paper 3},
   we show that the inclusion of a distant wall results in qualitatively different particle trajectories, demonstrative of the wall's singular perturbation.
   Specifically, the distance at which the wall significantly alters the particles interaction scales as $z_0^{3/5}$,
   where $z_0$ is the initial distance between the particle and the wall.
   The phase portrait of the particle relative paths admits domains of closed (dancing) and open (swapping) trajectories,
   apart from those that also exist in unbounded shear flows.
   We postulate that the patterns are topologically stable and verify it by direct numerical simulations of the Navier-Stokes equations.
   Qualitatively, the distant wall is the third body that changes the global topology of the phase portrait of the two-particle interaction.
}%
%
\graphicspath{{paper4/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

### 2020-02-26 paper5/paper.tex
To send for examination (oppo/comm).

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Droplets in homogeneous shear turbulence] % Short title used in headlines (optional)
{%
  Droplets in homogeneous shear turbulence% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Droplets in homogeneous shear turbulence} % Title for toc
%
\paperauthor[Rosti, Ge, Jain, Dodd, Brandt] % Short authors used in headlines and List Of Papers
{%
  Marco E. Rosti$^1$, Zhouyang Ge$^1$, Suhas S. Jain$^2$, \\Michael S. Dodd$^2$, Luca Brandt$^{1,3}$%
}%
%
\listpaperauthor{M.E. Rosti, Z. Ge, S.S. Jain, M.S. Dodd, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden\\%
  $^2$ Center for Turbulence Research, Stanford University, CA 94305, USA\\%
  $^3$ Department of Energy and Process Engineering, Norwegian University of Science and Technology (NTNU), NO 7491, Norway%
}%
%
\paperjournal[J. Fluid Mech.] % Short publish info used in List Of Papers
{%
	Journal of Fluid Mechanics%
}%
%
\papervolume{876}%
%
\papernumber{}%
%
\paperpages{962--984}%
%
\paperyear{2019}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   This paper reports a simulation study of liquid droplets immersed in a density- and viscosity-matched fluid (5\% volume fraction)
   in homogeneous shear turbulent flow at a shear Reynolds number equal to 15200.
   Detailed fluid motions are visualised, showing intense deformation, breakup and coalesence of the droplets as the flow evolves.
   We examine the flow and droplet statistics, including Taylor-microscale Reynolds numbers, turbulent kinetic energy budget, droplet size distributions, etc.,
   under various surface tensions and initial droplet diameters.
   The overall results suggest that the dispersed phase acts as a sink of the turbulent kinetic energy for the carrier fluid, and
   the maximal droplet sizes are predicted by the Hinze scaling despite of droplet coalescence and a mean shear.
}%
%
\graphicspath{{paper5/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

@@

%------------------------------------------------------------------------------
% Abstract
%------------------------------------------------------------------------------
%
\begin{paperabstract}
We  simulate  the  flow  of  two  immiscible  and  incompressible  fluids  separated  by  an interface  in  a  homogeneous  turbulent  shear  flow  at  a  shear  Reynolds  number  equal to  15 200.  The  viscosity  and  density  of  the  two  fluids  are  equal,  and  various  surface tensions  and  initial  droplet  diameters  are  considered  in  the  present  study.  We  show that  the  two-phase  flow  reaches  a  statistically  stationary  turbulent  state  sustained  by a  non-zero  mean  turbulent  production  rate  due  to  the  presence  of  the  mean  shear. Compared  to  single-phase  flow,  we  find  that  the  resulting  steady-state  conditions exhibit  reduced  Taylor-microscale  Reynolds  numbers  owing  to  the  presence  of  the dispersed  phase,  which  acts  as  a  sink  of  turbulent  kinetic  energy  for  the  carrier  fluid. At steady state, the mean power of surface tension is zero and the turbulent productionrate  is  in  balance  with  the  turbulent  dissipation  rate,  with  their  values  being  larger than  in  the  reference  single-phase  case.  The  interface  modifies  the  energy  spectrum by  introducing  energy  at  small  scales,  with  the  difference  from  the  single-phase  case reducing  as  the  Weber  number  increases.  This  is  caused  by  both  the  number  of droplets  in  the  domain  and  the  total  surface  area  increasing  monotonically  with  the Weber  number.  This  reflects  also  in  the  droplet  size  distribution,  which  changes  with the  Weber  number,  with  the  peak  of  the  distribution  moving  to  smaller  sizes  as  the Weber  number  increases.  We  show  that  the  Hinze  estimate  for  the  maximum  dropletsize,  obtained  considering  break-up  in  homogeneous  isotropic  turbulence,  provides an  excellent  estimate  notwithstanding  the  action  of  significant  coalescence  and  the presence  of  a  mean  shear.
\end{paperabstract}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Droplets in homogeneous shear turbulence] % Short title used in headlines (optional)
{%
  Droplets in homogeneous shear turbulence% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Droplets in homogeneous shear turbulence} % Title for toc
%
\paperauthor[Rosti, Ge, Jain, Dodd, Brandt] % Short authors used in headlines and List Of Papers
{%
  Marco E. Rosti$^1$, Zhouyang Ge$^1$, Suhas S. Jain$^2$, \\Michael S. Dodd$^2$, Luca Brandt$^{1,3}$%
}%
%
\listpaperauthor{M.E. Rosti, Z. Ge, S.S. Jain, M.S. Dodd, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden\\%
  $^2$ Center for Turbulence Research, Stanford University, CA 94305, USA\\%
  $^3$ Department of Energy and Process Engineering, Norwegian University of Science and Technology (NTNU), NO 7491, Norway%
}%
%
\paperjournal[J. Fluid Mech.] % Short publish info used in List Of Papers
{%
	Journal of Fluid Mechanics%
}%
%
\papervolume{876}%
%
\papernumber{}%
%
\paperpages{962--984}%
%
\paperyear{2019}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   This paper reports a numerical study of liquid droplets immersed in a density- and viscosity-matched fluid (5\% volume fraction)
   in homogeneous shear turbulent flow at a shear Reynolds number equal to 15200.
   Detailed fluid motions are visualised, showing intense deformation, breakup and coalesence of the droplets as the flow evolves.
   We examine the flow and droplet statistics, including Taylor-microscale Reynolds numbers, turbulent kinetic energy budget, droplet size distributions, etc.,
   under various surface tensions and initial droplet diameters.
   Two main conclusions drawn from the study are (i) the dispersed phase acts as a sink of the turbulent kinetic energy for the carrier fluid, and
   (ii) the maximal droplet sizes are predicted by the Hinze scaling despite of droplet coalescence and a mean shear.
}%
%
\graphicspath{{paper5/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

@@

%------------------------------------------------------------------------------
% Abstract
%------------------------------------------------------------------------------
%
\begin{paperabstract}
We  simulate  the  flow  of  two  immiscible  and  incompressible  fluids  separated  by  an interface  in  a  homogeneous  turbulent  shear  flow  at  a  shear  Reynolds  number  equal to  15 200.  The  viscosity  and  density  of  the  two  fluids  are  equal,  and  various  surface tensions  and  initial  droplet  diameters  are  considered  in  the  present  study.  We  show that  the  two-phase  flow  reaches  a  statistically  stationary  turbulent  state  sustained  by a  non-zero  mean  turbulent  production  rate  due  to  the  presence  of  the  mean  shear. Compared  to  single-phase  flow,  we  find  that  the  resulting  steady-state  conditions exhibit  reduced  Taylor-microscale  Reynolds  numbers  owing  to  the  presence  of  the dispersed  phase,  which  acts  as  a  sink  of  turbulent  kinetic  energy  for  the  carrier  fluid. At steady state, the mean power of surface tension is zero and the turbulent production rate  is  in  balance  with  the  turbulent  dissipation  rate,  with  their  values  being  larger than  in  the  reference  single-phase  case.  The  interface  modifies  the  energy  spectrum by  introducing  energy  at  small  scales,  with  the  difference  from  the  single-phase  case reducing  as  the  Weber  number  increases.  This  is  caused  by  both  the  number  of droplets  in  the  domain  and  the  total  surface  area  increasing  monotonically  with  the Weber  number.  This  reflects  also  in  the  droplet  size  distribution,  which  changes  with the  Weber  number,  with  the  peak  of  the  distribution  moving  to  smaller  sizes  as  the Weber  number  increases.  We  show  that  the  Hinze  estimate  for  the  maximum  droplet size,  obtained  considering  break-up  in  homogeneous  isotropic  turbulence,  provides an  excellent  estimate  notwithstanding  the  action  of  significant  coalescence  and  the presence  of  a  mean  shear.
\end{paperabstract}

### 2020-02-26 paper6/paper.tex
To send for examination (oppo/comm).

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Effective slip over partially filled microcavities] % Short title used in headlines (optional)
{%
  Effective slip over partially filled microcavities and its possible failure% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Effective slip over partially filled microcavities and its possible failure} % Title for toc
%
\paperauthor[Ge, Holmgren, Kronbichler, Brandt, Kreiss] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge$^1$, Hanna Holmgren$^2$, Martin Kronbichler$^3$, \\Luca Brandt$^1,$, Gunilla Kreiss$^2$%
}%
%
\listpaperauthor{Z. Ge, H. Holmgren, M. Kronbichler, L. Brandt, G. Kreiss}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden\\%
  $^2$ Division of Scientific Computing, Department of Information Technology, \\Uppsala University, Box 337, 751 05 Uppsala, Sweden\\%
  $^3$ Institute for Computational Mechanics, Technical University of Munich, Boltzmannstrasse 15, 85748 Garching b. München, Germany%
}%
%
\paperjournal[Phys. Rev. Fluids.] % Short publish info used in List Of Papers
{%
	Physical Review Fluids%
}%
%
\papervolume{3}%
%
\papernumber{054201}%
%
\paperpages{}%
%
\paperyear{2018}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   In this paper, we combined two separate simulation methods for a numerical study of the effective slip and robustness of the transverse flows over a liquid-infused surface (LIS). Computationally, we introduced a multiscale numerical framework to model wetting and interfacial flows by solving the Cahn-Hilliard equations within a Stokes system. Physically, we conducted a parametric study of the performance of a LIS, quantified by its effective slip length and potential drainage. Our results indicate that filling fraction is the most sensitive parameter for the effective slip, while more viscous lubricants tend to retain permanently in the surface cavities.
}%
%
\graphicspath{{paper6/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Effective slip over partially filled microcavities] % Short title used in headlines (optional)
{%
  Effective slip over partially filled microcavities and its possible failure% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Effective slip over partially filled microcavities and its possible failure} % Title for toc
%
\paperauthor[Ge, Holmgren, Kronbichler, Brandt, Kreiss] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge$^1$, Hanna Holmgren$^2$, Martin Kronbichler$^3$, \\Luca Brandt$^1$, Gunilla Kreiss$^2$%
}%
%
\listpaperauthor{Z. Ge, H. Holmgren, M. Kronbichler, L. Brandt, G. Kreiss}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden\\%
  $^2$ Division of Scientific Computing, Department of Information Technology, \\Uppsala University, Box 337, 751 05 Uppsala, Sweden\\%
  $^3$ Institute for Computational Mechanics, Technical University of Munich, Boltzmannstrasse 15, 85748 Garching b. München, Germany%
}%
%
\paperjournal[Phys. Rev. Fluids.] % Short publish info used in List Of Papers
{%
	Physical Review Fluids%
}%
%
\papervolume{3}%
%
\papernumber{054201}%
%
\paperpages{}%
%
\paperyear{2018}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   In this paper, we combine two simulation methods (phase field and level set) at separate scales to numerically study
   the transverse flow over a 2D model liquid-infused surface (LIS).
   Computationally, we introduce and verify a multiscale numerical framework for wetting modelling,
   which solves the Cahn-Hilliard equations in a local region near the moving contact line within a larger Stokes system.
   Physically, we conduct a parametric study of the LIS work performance, quantified by its effective slip length and potential drainage.
   Among the many parameters (the capillary number, viscosity ratio, contact angle, etc.) explored,
   we find that the filling fraction is the most sensitive parameter for the effective slip;
   the effects of other parameters are generally intertwined but weakened if the surface groove is not fully filled.
   In addition, we identify a shear-driven failure mode associated with the lubricant drainage,
   which is worse at higher lubricant viscosities if the lubricant is less viscous than the outer fluid,
   but seems to disappear if the lubricant is more viscous.
   Overall, we expect our study to serve as a conceptual guide for LIS design and call for further experimental tests to validate our findings.
}%
%
\graphicspath{{paper6/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

### 2020-02-26 paper7/paper.tex
To send for examination (oppo/comm).

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Note of HLGD for dense suspensions] % Short title used in healines (optional)
{%
 Implementation note on a minimal hybrid lubrication/granular dynamics model\\for dense suspensions% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Implementation note on a minimal hybrid lubrication/\\granular dynamics model for dense suspensions} % Title for toc
%
\paperauthor[Ge \& Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge \& Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, Department of Engineering Mechanics,\\
  KTH Royal Institute of Technology, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Technical Report] % Short publish info used in List Of Papers
{%
	Technical Report%
}%
%
\papervolume{}%
%
\papernumber{}
%
\paperpages{}%
%
\paperyear{2020}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   This report documents the implementation detail of a minimal hybrid lubrication/granular dynamics (HLGD) model
   intended for simulation of dense particle suspensions in shear flows.
   The method is meshless, explicit and solves directly the particle dynamics in the overdamped limit
   by balancing conservative and dissipative interactions at the pair level.
   Potential limitations include omissions of fluid/particle inertia and long-range hydrodynamic interactions.
   The implementation has been tested for $200\sim 500$ particles under volume fractions from 40\% to 64\%,
   showing jamming transition, continuous and discontinuous shear thickening that are in excellent agreement with literature results.
}%
%
\graphicspath{{paper7/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Note of HLGD for dense suspensions] % Short title used in healines (optional)
{%
 Implementation note on a minimal hybrid lubrication/granular dynamics model\\for dense suspensions% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Implementation note on a minimal hybrid lubrication/\\granular dynamics model for dense suspensions} % Title for toc
%
\paperauthor[Ge \& Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge \& Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, Department of Engineering Mechanics,\\
  KTH Royal Institute of Technology, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Technical Report] % Short publish info used in List Of Papers
{%
	Technical Report%
}%
%
\papervolume{}%
%
\papernumber{}
%
\paperpages{}%
%
\paperyear{2020}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   This report documents the implementation detail of a minimal hybrid lubrication/granular dynamics model
   intended for simulation of dense (potentially nonspherical) particle suspensions in shear flows.
   The method is meshless, explicit and solves directly the particle dynamics in the overdamped limit
   by balancing conservative and dissipative interactions at the pair level.
   Potential sources of inaccuracy include omissions of long-range hydrodynamic interactions and finite particle inertia due to numerical integration.
   The implementation is tested for $200\sim 500$ particles under volume fractions from 40\% to 64\%,
   showing jamming transition, continuous and discontinuous shear thickening that are in excellent agreement with literature results.
}%
%
\graphicspath{{paper7/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}
